Irt plot extra

### 2022-03-21 manuscript.Rmd
Minor typo corrected in the analysis plan

To validated the latent structure obtained in EFA, We conducted a categorical confirmatory factor analysis (CFA) with weighted least square with mean and variance adjusted (WLSMV) estimator estimator [@desjardinsHandbookEducationalMeasurement2018] on the data collected n our second round of data collection (CFA sample;n=`r nrow(CFA.descriptives)`). We assessed the model fit using common model fit guidelines: (i) $\chi^2$ test statistics: a non-significant test statistics is required to accept the model (ii) comparative fit index (CFI) and Tucker Lewis index (TLI):  close to .95 or above/ between 90-95 and above (iii) root mean square error of approximation (RMSEA): close to .06 or below, (iv) Standardized root mean square (SRMR): close to .08 or below [@huCutoffCriteriaFit1999; @schumacker2004beginner]. However, the $\chi^2$ test is sensitive to sample size [@brownConfirmatoryFactorAnalysis2015] and SRMR does not work well with ordinal data [@RN1272] As such, we judged the model fit using CFI, TLI, SRMR and RMSEA.

>>>>

To validated the latent structure obtained in EFA, We conducted a categorical confirmatory factor analysis (CFA) with weighted least square with mean and variance adjusted (WLSMV) estimator  [@desjardinsHandbookEducationalMeasurement2018] on the data collected n our second round of data collection (CFA sample;n=`r nrow(CFA.descriptives)`). We assessed the model fit using common model fit guidelines: (i) $\chi^2$ test statistics: a non-significant test statistics is required to accept the model (ii) comparative fit index (CFI) and Tucker Lewis index (TLI):  close to .95 or above/ between 90-95 and above (iii) root mean square error of approximation (RMSEA): close to .06 or below, (iv) Standardized root mean square (SRMR): close to .08 or below [@huCutoffCriteriaFit1999; @schumacker2004beginner]. However, the $\chi^2$ test is sensitive to sample size [@brownConfirmatoryFactorAnalysis2015] and SRMR does not work well with ordinal data [@RN1272] As such, we judged the model fit using CFI, TLI, SRMR and RMSEA.
